To be FAIR: Theory Specification Needs an Update

### 2025-06-20 action_letter.Rmd
added link to revision regarding phonological loop
Update action_letter.Rmd

**DO THIS, ANDREAS?**

@@

We respectfully disagree; open data - one example of modular publishing - has increased dramatically in recent decades, in psychology the percentage of articles that share data has increased from ~7% in 2000–2009 to ~50% in 2010-2019. In other disciplines, the increase has been even larger (up to ~80%).
Given this, we don't see a reason to note this as a limitation, but we have added a reference that indicates that data sharing has become widely adopted in psychology:

@@

> We are particularly endebted to our Reviewer, Dr. Eric Turkheimer, whose thoughtful reflections on FAIR theory were incorporated into the Discussion.

>>>>

We added a brief description and a reference as suggested:

`r get_revision("phonoloop")`

@@

We respectfully disagree; Open Data - one example of modular publishing - has increased dramatically in recent decades. In Psychology the percentage of articles that share data openly has increased from ~7% in 2000–2009 to ~50% in 2010-2019. In other disciplines, the increase has been even larger (up to ~80%).
Given this, we don't see a reason to note this as a limitation, but we have added a reference that indicates that data sharing has become widely adopted in Psychology:

@@

> We are particularly indebted to one of our reviewers, Dr. Eric Turkheimer, whose thoughtful reflections on FAIR theory were incorporated into the Discussion.
